The very idea of the Google bug bounty / Vulnerability Reward program (VRP) stemmed from the approach Donald Knuth, the creator of the typing system used by this very paper you're reading  \cite{GoogleBugHunters}  \\
Back in the 70s he just kept on going for (perhaps) way too long perfecting his book "The art of computer programming", so he thought maybe it'd be a better idea to let the people submit erratas for money. Thus, a primitive form of "bug bounty" program was born. \\
Maybe try to ship fast, and allow the people to review and correct your insecure code, rewarding them for it. \\
Now, the folks over at google established a formal set of criteria by which basement-dwellers have to abide.

\hrule
All of the following rules and regulations can be found here: \cite{google_bughunters_invalid_reports}, \cite{google_bughunters_report} , \cite{google_bughunters_rules}, and are have specific details, that differ wether you're submitting a report for an Android, Chrome, Google or some of their open source products.
\subsection{Hacker Workflow ($\mathcal{W}_{\text{Hacker}}$)}
\begin{enumerate}[label=\textbf{\arabic*}., itemsep=4pt]
    \item \textbf{Prep \& Discovery:}  
    Review VRP scope/rules and look for in-scope, fixable issues.
    
    \item \textbf{Report Submission ($\mathcal{R}$):}  
    Send a clear report with repro steps, PoC, and impact.

    \item \textbf{Coordinated Disclosure:}  
    Keep findings private until Google patches them.

    \item \textbf{Rewards:}  
    Valid in-scope bugs earn monetary rewards ($M$), possible bonuses ($B$), and Hall of Fame credit ($H$).
\end{enumerate}

\hrule

\subsection{Google Workflow ($\mathcal{W}_{\text{Google}}$)}
\begin{enumerate}[label=\textbf{\arabic*}., itemsep=4pt]
    \item \textbf{Triage ($T$):}  
    Acknowledge the report, reproduce the bug, check scope and duplicates.

    \item \textbf{Severity ($S$):}  
    Rate impact and exploitability; assign Critical/High/Med/Low.

    \item \textbf{Fix ($P$):}  
    Engineering team patches the issue and deploys the fix.

    \item \textbf{Reward ($M$):}  
    VRP panel reviews severity and issues payment:  
    $M = \text{BaseReward}(S) + B$.
\end{enumerate}

\hrule

\subsection{VRP Lifecycle}
\[
\mathcal{R}_{\text{Submit}}
\rightarrow T
\rightarrow S
\rightarrow P
\rightarrow M
\]

\noindent
Where $\mathcal{R}$ = report, $T$ = triage, $S$ = severity, $P$ = patch, $M$ = reward.


\subsection{An examplee noww}
There's an infamous hacker going around their bug bounty programs, that seems to be romanian: \cite{inspector-ambitious}, but he doesn't publish his reports unfortunately, so I'll instead talk about \cite{NDevTK}, who, out of all of the top spots, actually publishes their findings and replicability steps. \\

This exploit has to do with the way Google's old GitHub competitor was parsing their ... blabla si de aici nu prea mai stiu sincer vad eu dupa

